Modular Deep Encoder-Decoders

### 2016-04-26 paper/proposal.tex
Added latex sources.

We used the freely available dataset from
\url{https://github.com/ParallelMazen/SaudiNewsNet} The dataset contains
a total of 31,030 Arabic newspaper articles, with title, author, date,
url and content in each entry. Article objects are reprensented in json
format, with UTF-8 encoding. We wrote a script to download the data from
github repo, unzip each file, and read them in as json objects. The
function can also give out content by key values such as title, author
and etc.

@@

The procedure is quite straight-forward. While part of the team worked
on building our tailored dataset, the other half worked on the model
definition and training procedure.

Once every pre-requisite is available, we trained the first encoder
$E_1$ (implemented as a recurrent neural network) to build the embedding
$V_1$. Since we only dealt with a relatively simple classification task,
our decoder $D_1$ was simply a fully connected multi-layer perceptron.
They were jointly trained end-to-end by propagating the gradients
through the embedding from $D_1$ to $E_1$.

The second training step was to train the second encoder $E_2$. Again,
we also performed training end-to-end, but specifically did not
propagate the gradients through $E_1$.

@@

\section{Results}\label{results}

\section{Discussion}\label{discussion}

>>>>

We will use the freely avaiable dataset from
\url{https://github.com/ParallelMazen/SaudiNewsNet} and extract the
titles and articles content. Since the dataset initial purpose is not
the classification, we will have to slightly rework it to fit our
purpose.

We will use the neon python library for training deep networks. In the
case where the training phase would become too expensive, we will also
rely on the mpi4py library.

@@

The procedure is quite straight-forward. While part of the team will
work on building our tailored dataset, the other half will work on the
model definition and training procedure. Coordination at the beginning
of the work will be curcial. In particular, we plan on feeding the text
data as a sequence of one-hot character encodings.

Once every pre-requisite is available, we will train the first encoder
$E_1$ (implemented as a recurrent neural network) to build the embedding
$V_1$. Since we will only be dealing with a relatively simple
classification task, our decoder $D_1$ will simply be a fully connected
multi-layer perceptron. They will be jointly trained end-to-end by
propagating the gradients through the embedding from $D_1$ to $E_1$.

The second training step will be to train the second encoder $E_2$.
Again, we also perform training end-to-end, but specifically do not
propagate the gradients through $E_1$. We hope to avoid optimizing the
parameters of $D_1$, but this might not be practically doable.

@@

The final evaluation scheme is mostly to be determined depending on our
obtained outcomes. Obviously, we want to compare the new model with the
the the jointly trained one, as well as a classification baseline.

\section{Participants \& Labor
Division}\label{participants-labor-division}

The participants in alphabetical order:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Seb Arnold - 9013085897 - arnolds@usc.edu
\item
  Prashanth Gurunath Shivakumar - 2251924199 - pgurunat@usc.edu
\item
  Qiangui Huang - 9532576000 - qianguih@usc.edu
\item
  Cheng Qu - 2385279985 - chengqu@usc.edu
\end{itemize}

Instead of having a fixed division of the labor, we assigned one
responsible to each task. The responsible acts as a project lead on the
designed task and other team members can contrbibute to the task as
required.

\begin{itemize}
\item
  Dataset: Cheng
\item
  Model Training: Quiangui
\item
  Knowledge Transfer: Seb
\item
  Report Writing: Prashanth
\end{itemize}
